Untitled

### 2024-10-23 log.Rmd
working on fixing functions using GNR

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Date: 
clipr::write_clip(paste0('## ', format(Sys.time(), "%F (%A %B %e)\n\n")))
# Date and time:
clipr::write_clip(paste0('## ', format(Sys.time(), "%F %X %Z (%A %B %e)\n\n")))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Date: 
clipr::write_clip(paste0('## ', format(Sys.time(), "%F (%A %B %e)\n\n")))
# Date and time:
clipr::write_clip(paste0('## ', format(Sys.time(), "%F %X %Z (%A %B %e)\n\n")))
```
## 2024-10-16 (Wednesday October 16)

Working on updating `scrapenames`.
The options have been updated, but it has not been tested.

## 2024-10-04 (Friday October  4)

It seems some of the functions that use the Global Names APIs no longer work. 
There seem to be multiple APIs (and corresponding command line tools) with multiple endpoints, so its hard to tell which is the new version for presumably depreciated APIs.
I will look into each of the API/tools.

* GNFinder: searches for latin names in text. Seems intended to provide metadata about species mentioned in old publications. Results can be passed to GNVerifier.
* GNVerifier: Used to provide the currently accepted name for a species.
